Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-07 paper/main.tex
Started on results chapter. Missing the acutal graphs.

\section{Modifications to the Tahoe-\ac{LAFS} Code}

@@

The performance measurements were only performed on the Tahoe client, and not on
the storage servers. We motivated this by looking at the system performance
graphs of the storage nodes during upload and retrieval, where neither the
\ac{CPU}, network, disk or memory usage runs out of capacity. The \ac{CPU} usage
during testing on one of the storage nodes is depicted in Figure
\ref{fig:munin:storagenode}.

@@

% Maybe cite
% \url{http://tahoe-lafs.org/trac/tahoe-lafs/wiki/Performance?version=32}

% Munin?

@@

In this chapter, we will focus on the concrete results derived from our testing.

\section{Test scope}
% What is tested and what is not tested?
Immutable files are not tested, move text from Section 3.3.3.

\section{Measuring Performance}
Include code from hashutil.py and the use of time in bash.

\section{\ac{SUPERCOP} benchmarks}
% TODO: more introduction text here.

The results of \ac{SHA}-3 256-bit functions and \ac{SHA}-256 benchmarking in
\ac{SUPERCOP} can be seen in tables \ref{tbl:supercop:long},
\ref{tbl:supercop:4096}, \ref{tbl:supercop:1536}, \ref{tbl:supercop:576},
\ref{tbl:supercop:64} and \ref{tbl:supercop:8}. The lower the numbers, the
faster the algorithms performed in the test.

@@

% This chapter should contain (in listed and grouped order):
% -----------------------------------------------------------
% Describe inconsitencies in the numbers, and try to explain them.
%
% Compare our results with general (supercop) results.
% Optimized candidates - which gain could be expected from more optimized
%   candidates?
% Mention that some SUPERCOP candidates are missing UPDATE-functionality.
%
% How much gain can Tahoe-LAFS get by switching to SHA-3?
% Time gain of removing ``double'' SHA-256. Double only in digest().
%
% Implications of only testing immutable files? (mutable files also
%   include directories)
% Adding a capability to support new hash functions in tahoe. (Our
%   current way breaks backwards compatability)
%
% What if we had used another coding scheme? - does Cython lower the
%   candidates performance?
%
% More general stuff. What could have been done differently?

>>>>

\section{Modifications to the Tahoe-\ac{LAFS} Code}
\label{sec:modtahoe}

@@

The performance measurements were only performed on the Tahoe client, and not on
the storage servers. We motivated this by looking at the system performance
graphs of the storage nodes during upload and retrieval, where neither the
\ac{CPU}, network, disk or memory usage raise towards maximum threshold. The
\ac{CPU} usage during testing on one of the storage nodes is depicted in Figure
\ref{fig:munin:storagenode}.

@@

% FIXME: Decide whether Munin should be included?

@@

In this chapter, we will focus on the concrete results derived from our testing.
The method of testing is described, along with the test scope.

Further on, we exhibit the results from the \ac{SUPERCOP} benchmark, before
presenting the graphs of how much time the hashing operations take when
downloading and uploading a number of different test vectors, and show these
data in relation to other measurements, such as total operation time.

\section{Test scope}

As stated in Section \ref{sec:modtahoe}, only immutable files are tested. The
mutable files are not tested because of our way of integrating the SHA-3
candidates within the Tahoe-LAFS code.

To measure the performance impact of the different implementations, we time the
hash function calls from Tahoe, in addition to timing the total operation time,
e.g. the total time it takes for a 1GB file to be uploaded to grid.

\section{Measuring Performance}

Listing \ref{lst:hashutil_time} demonstrates the use of the {\verb time } module
in Python. On every call to {\verb update() } or {\verb digest() }, a variable
is increased with the time it took to run the underlying hash library
functionality. Similarly, Listing \ref{lst:testrunner} shows the use of the
{\verb date } command to calculate the number of seconds it takes it takes for
Tahoe to put a file to the grid.

\lstinputlisting[label=lst:hashutil_time, caption=Timing in Python (extraction from hashutil.py)]
{listings/hashutil_timing.py}

\lstinputlisting[language=sh, label=lst:testrunner, caption=Timing in Bash from test runner]
{listings/test_runner.sh}

\section{\ac{SUPERCOP} benchmarks}
% TODO: more introduction text here?

The results of the \ac{SHA}-3 256-bit functions and \ac{SHA}-256 benchmarking in
\ac{SUPERCOP} can be seen in tables \ref{tbl:supercop:long},
\ref{tbl:supercop:4096}, \ref{tbl:supercop:1536}, \ref{tbl:supercop:576},
\ref{tbl:supercop:64} and \ref{tbl:supercop:8}. The lower the numbers, the
faster and better the algorithms performed in the test.

@@

% This chapter should contain (in listed and grouped order):
% -----------------------------------------------------------
% Describe inconsitencies in the numbers, and try to explain them.
%
% Compare our results with general (supercop) results.
% Optimized candidates - which gain could be expected from more optimized
%   candidates?
% Mention that some SUPERCOP candidates are missing UPDATE-functionality.
%
% How much gain can Tahoe-LAFS get by switching to SHA-3?
% Time gain of removing ``double'' SHA-256. Double only in digest().
%
% Implications of only testing immutable files? (mutable files also
%   include directories)
% Adding a capability to support new hash functions in tahoe. (Our
%   current way breaks backwards compatability)
%
% What if we had used another coding scheme? - does Cython lower the
%   candidates performance?
%
% More general stuff. What could have been done differently? Critisize
% ourselves.
